VFTS682: a confirmed dynamical ejection?

### 2018-05-09 VFTS682.tex
./aa.cls

@@

>>>>

For each of the two local rest frames (``surroundings'' and ``R136
cluster''), we compute the average transverse velocity as:

\begin{equation}
  \label{eq:mean}
  \langle \mu_i\rangle = \frac{\sum_\mathrm{stars}\frac{1}{\Delta
      \mu_i}\mu_i}{\sum_\mathrm{stars} \frac{1}{\Delta \mu_i}} \ \ , \
  \ \Delta \langle \mu_i\rangle = \frac{\sqrt{N}}{\sum_\mathrm{stars}
    \frac{1}{\Delta \mu_i}} \ \ ,
\end{equation}
where $i = \mathrm{RA}, \mathrm{DEC}$, and $\Delta \mu_i$ is the error
on the proper motion component reported by Gaia, and the sums run over
all the $N$ stars of the frame considered. We evaluate each proper motion
component separately.

@@

\subsection{Is it a runaway star?}
We first address the question of whether VFTS682 is a typical star in
its surroundings from the kinematic point of view, or whether it is a
runaway star with a significantly large peculiar velocity. The former is what should
be expected if it formed where we observe it today, in relative
isolation from other massive stars. We calculate the velocity relative
to the general population in its surroundings, shown as blue dots in
the large panel of\Figref{fig:main}, assuming a distance of
$D=50$\,kpc.

\todo{discuss numbers found, refer to figure}
likely conclusion looking at the general region: it is a ``bona
  fide'' runaway star with velocity components $\left(v_\mathrm{RA},
  v_\mathrm{DE}, v_\mathrm{rad}\right) = \left(\todo{XX},\todo{YY},
  \todo{ZZ}\right)$, corresponding to $v\equiv\sqrt{v_\mathrm{RA}^2+v_\mathrm{DE}^2+v_\mathrm{rad}^2}=\todo{AA}\,\kms$.

\subsection{Does it come from the R136 cluster?}
The inset plot in \Figref{fig:main} shows a zoom in of the region
around R136 which includes VFTS682. To test the hypothesis that the
star was indeed ejected from this region, we check the relative
orientation of its proper motion. The error cone, obtained by
propagating the errors on the proper motion components indicates that
R136 is indeed the most likely origin, as expected by \cite{fujii:11,
  banerjee:12}.

\todo{kinematic age}
